Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-08 arxiv/intro.tex
introduction wip

\begin{abstract}
	Hard parameter sharing is a widely used approach to learn from multiple tasks in many applications, such as text classification.
	The idea is that all tasks share the same feature layer, while each task uses a specific output layer for prediction.
	Intuitively, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
	Yet, rigorously formulating such intuition can be technically challenging.
	This paper analyzes the generalization performance of hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
	We present tight generalization bounds
	%that scale with datasets' sample sizes and the spectrum of their feature covariates
	for two canonical cases:
	(i) multiple tasks with the same feature covariates;
	(ii) two tasks with arbitrarily different sample sizes and covariance matrices.
	We also demonstrate that these estimates for the empirical loss of hard parameter sharing are incredibly accurate in modest dimensions.
	Finally, we apply our results to explain several intriguing phenomena; for example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
	This suggests progressively adding data as a more efficient procedure for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
%	Multi-task learning is a powerful approach in many applications such as image and text classification. Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning. In this work, we provide a rigorous study to answer the question in the high-dimensional linear regression setting. We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer, and develop new concentration bounds to analyze the tradeoff. Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting. We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased sample ratio, and covariate shift under increased sample ratio. We validate the three effects on text classification tasks. Inspired by our theory, we show two practical connections of interest.
%	First, single-task results can help to understand when multi-task learning gives gains. Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
\end{abstract}

>>>>

\begin{abstract}
	Hard parameter sharing is a widely used approach to learn from multiple tasks in many applications, such as text classification. The idea is that all tasks share the same feature layer, while each task uses a specific output layer for prediction. Intuitively, the performance of hard parameter sharing depends on dataset properties such as their sample sizes. Yet, rigorously formulating such intuition can be technically challenging. This paper analyzes the generalization performance of hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio. We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices. We also demonstrate that these estimates for the empirical loss of hard parameter sharing are incredibly accurate in modest dimensions. Finally, we explain several intriguing empirical phenomena. For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
%	Multi-task learning is a powerful approach in many applications such as image and text classification. Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning. In this work, we provide a rigorous study to answer the question in the high-dimensional linear regression setting. We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer, and develop new concentration bounds to analyze the tradeoff. Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting. We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased sample ratio, and covariate shift under increased sample ratio. We validate the three effects on text classification tasks. Inspired by our theory, we show two practical connections of interest.
%	First, single-task results can help to understand when multi-task learning gives gains. Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
\end{abstract}
